DNSKEY Management

### 2012-12-03 paper/paper.tex
Add more info about ch.

\section{Case-Study: Switzerland (\texttt{ch.} Zone)\wbts}
\label{sec:case-study}
According to a query on \cite{secspider}, the \verb|ch.| TLD zone is signed and
fully veryfiable from the root zone anchor. The validity period of a
zone signing key is 37 days \cite{switch10}.

>>>>

\section{Case-Study: Switzerland (\texttt{ch.} Zone)\wbts}
\label{sec:case-study}

\paragraph{Certificate Chain} According to a query on
\cite{secspider}, the \verb|ch.| TLD zone is signed and fully
veryfiable from the root zone anchor on downwards. The certificate
chain can hence fully be established and no separate TARs are
required.

\paragraph{Rollover} The validity period of a zone signing key (for
\verb|ch.|) is 37 days \cite{switch10}. For child zones,  DNSSEC and
DNSKEY entries can be enabled and disabled through SWITCH's
web-interface which is able to pull the keys automatically from the
authoritative DNS servers. It is therefore relatively simple to enable
DNSSEC for a \verb|x.ch.| zone, but using the web-interface might be
cumbersome when having to deal with rollovers for a large number of
domains.
